---
title: "Databel"
author: "Bryant Jay"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Adding the data.

#### Set up work environment.

```{r prep, warning = FALSE, message=FALSE}
library(caret)
library(tidyverse)

set.seed(999)

setwd("C:/Users/sbrya/Documents/random_data/databel_churn")
```

#### Set up the data
With readr.

```{r readr}
databel <- read_csv(
  "databel.csv",
  col_types = "cfiidddffdidfdfcfifffifffddff"
)
```

Change field names to a more usable format for R.

``` {r names}
databel <- databel %>%  
  select_all(~gsub("\\s+|\\.", "_", .)) %>%
  select_all(~gsub("\\(|\\)", "", .)) %>%
  select_all(~gsub("\\&", "and", .)) %>%
  select_all(tolower)
```

#### Data Preview

```{r data_preview}
glimpse(databel)
summary(databel)
```

Changing data to more code-friendly formats.

```{r data_readability}
databel <- databel %>%
   mutate(payment_method = factor(str_replace_all(databel$payment_method, " ", "_" )),
          churn_reason = factor(str_replace_all(databel$churn_reason, " ", "_" )),
          contract_type = factor(str_replace_all(str_replace_all(databel$contract_type, " ", "_" ), "-", "_" )),
          gender = factor(str_replace_all(databel$gender, " ", "_" )),
          intl_active = ifelse(databel$intl_active == "Yes", 1, 0),
          intl_plan = ifelse(databel$intl_plan == "yes", 1, 0),
          unlimited_data_plan = ifelse(databel$unlimited_data_plan == "Yes", 1, 0),
          under_30 = ifelse(databel$under_30 == "Yes", 1, 0),
          senior = ifelse(databel$senior == "Yes", 1, 0),
          group = ifelse(databel$group == "Yes", 1, 0),
          device_protection_and_online_backup = ifelse(databel$device_protection_and_online_backup == "Yes", 1, 0),
          needs_intl_plan = ifelse(databel$intl_active == 1 & databel$intl_plan == 0, 1, 0),
          does_not_need_intl_plan  = ifelse(databel$intl_active == 0 & databel$intl_plan == 1, 1, 0),
          CA_resident = ifelse(state == "CA", 1, 0)
   )
```



Removing unnecessary columns in preparation for modeling. Customer ID and Customer Phone number are individually distinct character fields which will slow model performance. Churn category and churn reason are also not needed, as these values are only collected from know cases of churn after they occur, and cannot be used as predictors.

Labels with missing values are removed.

```{r}
db_sample <- databel %>% dplyr::select(-customer_id, -phone_number, - churn_category, -churn_reason)
db_sample <- drop_na(db_sample)
```
Taking a smaller sample.

```{r sampling}
sample <- createDataPartition(y = db_sample$churn_label, p = 0.2, list = FALSE)
db_select <- db_sample[sample, ]

db_copy <- db_select
```

```{r}
in_train <- createDataPartition(y = db_select$churn_label, p = 0.7, list = FALSE)
train <- db_select[in_train, ]
test  <- db_select[-in_train, ]
```

```{r}
#log model

logistic_model <- train(churn_label ~ ., data = train, method = "glm",
                        family = binomial, preProcess = c("center", "scale", "nzv"))

logistic_pred <- predict(logistic_model, newdata = test)
summary(logistic_model)

confusionMatrix(logistic_pred, test$churn_label)
```